Wibbly Wobbly Timely Wimely Questions: \\Classifying Timely And Timeless Questions

### 2021-07-16 paper/main.tex
comments

@@

\jbgcomment{Cite followon datasets}

We used Google’s Natural Questions (NQ) dataset \cite{nqdataset}. The
dataset has been used for open-domain question answering research, and
is “the first large publicly available dataset to pair real user
queries with high quality annotations of answers in documents”. It
consists of 307,373 anonymized natural questions asked via the Google
search engine, and each question is paired with the full HTML markup
of a Wikipedia page. Human annotators have marked the location of long
and short answers to each question. A model that is trained on the NQ
dataset is required to read the full Wikipedia article, and locate the
answers. From our analysis, we estimate that less than 10\% of the
questions were timely questions.

Natural Questions is unique becuase it has been updated twice: once by
\abr{nq}'s original authors for the Efficient \abr{qa} competition and
by \abr{ai2} by a new collection of questions from Google.

@@

@@

@@

\subsubsection{Answer Filtering}
After getting an answer for each year, we hypothesized that a timely question
would have answers that change year to year, while a timeless question would
have similar answers no matter which year was used as the context. However,
before we could identify changes with the answers, we had to account for errors
with the model’s ability to answer questions. First, we removed any questions in
which any of the answers returned a page that did not exist, or was redirected.
Although a page that did not exist could indicate a timely question, we decided
to remove those in case there was a problem with the Wikipedia link or the
model. \begin{figure*}[ht]
	\begin{center}
		\includegraphics[width=5in]{timeless leven.png}
		\includegraphics[width=5in]{timely leven.png}
		\includegraphics[width=5in]{leven false pos.png}
		\includegraphics[width=5in]{leven_false_neg.PNG}
	\end{center}
	\caption{Levenshtein Examples (top is timeless, middle is timely, third is false positive, bottom is false negative).}
	\label{fig:levenshtein_examples}
\end{figure*}

@@

@@

@@

>>>>

\jbgcomment{Given this more formal definition, }

@@

\jbgcomment{Cite followon datasets, incorporate them into the analysis as test data}

We use Google’s Natural Questions (NQ) dataset \cite{nqdataset}. The
dataset has been used for open-domain question answering research, and
is “the first large publicly available dataset to pair real user
queries with high quality annotations of answers in documents”. It
consists of 307,373 anonymized natural questions asked via the Google
search engine, and each question is paired with the full HTML markup
of a Wikipedia page. Human annotators have marked the location of long
and short answers to each question. A model that is trained on the NQ
dataset is required to read the full Wikipedia article, and locate the
answers. From our analysis, we estimate that less than 10\% of the
questions were timely questions.

Natural Questions is unique becuase it has been updated twice: once by
\abr{nq}'s original authors for the Efficient \abr{qa} competition and
by \abr{ai2} by a new collection of questions from Google.  The source
of the questions are the same, which allows these followon datasets to
serve as test sets to validate our ability to detect timely questions.

@@

\jbgcomment{Before going into the string measurement distances,
  motivate why you need them (need to compare answers) and then
  discuss why ``standard'' things like exact match don't work.}

@@

\jbgcomment{I think this would be stronger by working through an
  example.  take a question, find the relevant passage, and show how
  it changes when there's a timely question.}

@@

\subsubsection{Answer Filtering}

\jbgcomment{Give the main idea first, then go into details like redirects and things like that.}

After getting an answer for each year, we hypothesized that a timely question
would have answers that change year to year, while a timeless question would
have similar answers no matter which year was used as the context. However,
before we could identify changes with the answers, we had to account for errors
with the model’s ability to answer questions. First, we removed any questions in
which any of the answers returned a page that did not exist, or was redirected.
Although a page that did not exist could indicate a timely question, we decided
to remove those in case there was a problem with the Wikipedia link or the
model. \begin{figure*}[ht]
	\begin{center}
		\includegraphics[width=5in]{timeless leven.png}
		\includegraphics[width=5in]{timely leven.png}
		\includegraphics[width=5in]{leven false pos.png}
		\includegraphics[width=5in]{leven_false_neg.PNG}
	\end{center}
	\caption{Levenshtein Examples (top is timeless, middle is timely, third is false positive, bottom is false negative).}
	\label{fig:levenshtein_examples}
\end{figure*}

@@

\jbgcomment{It seems like it might be better to cut the edit distance stuff and just focus on BLEU?}

@@

\jbgcomment{Would running DPR over the whole dump address the filtering problems?}

@@

\jbgcomment{Even if there aren't more datasets for the workshop
  submission, would be good to talk about other datasets, using DPR to
  improve recall of timely questions.}
